---
title: "report"
author: "Abu Saleh Mosa Faisal"
date: "6/17/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```





## For Gleason Score 7

```{r, include=FALSE}
df_case_7= subset(df_combined, gleason_score == 7 & CaseControl == "Case")
## Control

df_control= subset(df_combined, CaseControl == "Control")

df_control_gene = df_control[,1:20531]

df_control.new= df_control_gene%>% remove_rownames %>% column_to_rownames(var="sampleID")
df_controlgene= as.data.frame(t(df_control.new))
head(df_controlgene)


#df_cong_7$Means <-apply(df_cong_7,1,mean)


## Case


df_case_7gene = df_case_7[,1:20531]

df_case.7= df_case_7gene%>% remove_rownames %>% column_to_rownames(var="sampleID")
df_cg_7= as.data.frame(t(df_case.7))
head(df_cg_7)




```

```{r, include=FALSE}
df_c= cbind(df_cg_7, df_controlgene)

head(df_c)
```





```{r, include=FALSE}
ttestgene <- function(df, grp1, grp2) {
  x = df[grp1]
  y = df[grp2]
  x = as.numeric(x)
  y = as.numeric(y)  
  results = t.test(x, y)
  results$p.value
}
rawpvalue = apply(df_c, 1, ttestgene, grp1 = c(1:247), grp2 = c(248:300))
```


```{r, include=FALSE}
control1 = apply(df_controlgene, 1, mean)
test1= apply(df_cg_7, 1, mean) 
#confirming that we have a vector of numbers
class(control1) 
class(test1)
```


```{r, include=FALSE}
#because our data is already log2 transformed, we can take the difference between the means.  And this is our log2 Fold Change or log2 Ratio == log2(control / test)
Log2foldchange<- control1 - test1 
```


```{r, echo=FALSE}
hist(Log2foldchange, xlab = "log2 Fold Change (Control vs Test)")
```




```{r, include=FALSE}

results = cbind(Log2foldchange, rawpvalue)
results = as.data.frame(results)
results$genename <- rownames(results)

library(ggplot2)
volcano = ggplot(data = results, aes(x = Log2foldchange, y = -1*log10(rawpvalue), label=genename))
volcano + geom_point() + geom_text(hjust=0, vjust=0) + theme_minimal() + geom_vline(xintercept=c(-0.6, 0.6), col="red") +
    geom_hline(yintercept=-log10(0.05), col="red")
  
```





```{r, include=FALSE}
# add a column of NAs
results$diffexpressed <- "NO"
# if log2Foldchange > 0.6 and pvalue < 0.05, set as "UP" 
results$diffexpressed[results$Log2foldchange > 0.6 & results$rawpvalue < 0.05] <- "UP"
# if log2Foldchange < -0.6 and pvalue < 0.05, set as "DOWN"
results$diffexpressed[results$Log2foldchange <   -0.6 & results$rawpvalue < 0.05] <- "DOWN"
```


```{r, include=FALSE}
# Re-plot but this time color the points with "diffexpressed"
p <- ggplot(data=results, aes(x=Log2foldchange, y=-log10(rawpvalue), col=diffexpressed)) + geom_point() + theme_minimal()

# Add lines as before...
p2 <- p + geom_vline(xintercept=c(-0.6, 0.6), col="red") +
        geom_hline(yintercept=-log10(0.05), col="red")


## Change point color 

# 1. by default, it is assigned to the categories in an alphabetical order):
p3 <- p2 + scale_color_manual(values=c("blue", "black", "red"))

# 2. to automate a bit: ceate a named vector: the values are the colors to be used, the names are the categories they will be assigned to:
mycolors <- c("blue", "red", "black")
names(mycolors) <- c("DOWN", "UP", "NO")
p3 <- p2 + scale_colour_manual(values = mycolors)
```

```{r, echo=FALSE}
# Now write down the name of genes beside the points...
# Create a new column "delabel" to de, that will contain the name of genes differentially expressed (NA in case they are not)
results$delabel <- NA
results$delabel[results$diffexpressed != "NO"] <- results$genename[results$diffexpressed != "NO"]

ggplot(data=results, aes(x=Log2foldchange, y=-log10(rawpvalue), col=diffexpressed, label=delabel)) + 
    geom_point() + 
    theme_minimal() +
    geom_text() +
    geom_vline(xintercept=c(-0.6, 0.6), col="red") +
    geom_hline(yintercept=-log10(0.05), col="red")
```











```{r, include=FALSE}
Upregulatedgenes = Log2foldchange[Log2foldchange > 0.6 ]
Downregulatedgenes = Log2foldchange[Log2foldchange<  -0.6]

Upreg_genes = attr(Upregulatedgenes, "names")
Downreg_genes= attr(Downregulatedgenes, "names")


```

```{r, include=FALSE}

##From result Table
results

Upreg_7= results[results$Log2foldchange > 0.6 & rawpvalue < 0.05, ]
Upreg_7

Downreg_7 = results[results$Log2foldchange <= -0.6 & rawpvalue < 0.05, ]
Downreg_7
```







```{r, echo=FALSE}
# Finally, we can organize the labels nicely using the "ggrepel" package and the geom_text_repel() function
# load library
library(ggrepel)
# plot adding up all layers we have seen so far
ggplot(data=results, aes(x=Log2foldchange, y=-log10(rawpvalue), col=diffexpressed, label=delabel)) +
        geom_point() + 
        theme_minimal() +
        geom_text_repel() +
        scale_color_manual(values=c("blue", "black", "red")) +
        geom_vline(xintercept=c(-0.6, 0.6), col="red") +
        geom_hline(yintercept=-log10(0.05), col="red")
```
**Total number of Upregulated genes : 3198**
**Total number of Downregulated genes : 1585**




#################################################################################





## For Gleason Score 8

```{r, include=FALSE}
df_case_8= subset(df_combined, gleason_score == 8 & CaseControl == "Case")

df_case_8gene = df_case_8[,1:20531]

df_case.8= df_case_8gene%>% remove_rownames %>% column_to_rownames(var="sampleID")
df_cg_8= as.data.frame(t(df_case.8))
head(df_cg_8)

```

```{r, include=FALSE}
df_c8= cbind(df_cg_8, df_controlgene)

head(df_c8)
```



```{r, include=FALSE}
ttestgene <- function(df, grp1, grp2) {
  x = df[grp1]
  y = df[grp2]
  x = as.numeric(x)
  y = as.numeric(y)  
  results = t.test(x, y)
  results$p.value
}
Rawpvalue = apply(df_c8, 1, ttestgene, grp1 = c(1:64), grp2 = c(65:117))
```


```{r, include=FALSE}
control8 = apply(df_controlgene, 1, mean)
test8= apply(df_cg_8, 1, mean) 
#confirming that we have a vector of numbers
class(control8) 
class(test8)
```


```{r, include=FALSE}
#because our data is already log2 transformed, we can take the difference between the means.  And this is our log2 Fold Change or log2 Ratio == log2(control / test)
log2foldchange<- control8 - test8 
```





```{r, echo=FALSE}
hist(log2foldchange, xlab = "log2 Fold Change (Control vs Case)")
```






```{r, include=FALSE}

results = cbind(log2foldchange, Rawpvalue)
results = as.data.frame(results)
results$genename <- rownames(results)

library(ggplot2)
volcano = ggplot(data = results, aes(x = log2foldchange, y = -1*log10(Rawpvalue), label=genename))
volcano + geom_point() + geom_text(hjust=0, vjust=0) + theme_minimal() + geom_vline(xintercept=c(-0.6, 0.6), col="red") +
    geom_hline(yintercept=-log10(0.05), col="red")
  
```


```{r, include=FALSE}
# add a column of NAs
results$diffexpressed <- "NO"
# if log2Foldchange > 0.6 and pvalue < 0.05, set as "UP" 
results$diffexpressed[results$log2foldchange > 0.6 & results$Rawpvalue < 0.05] <- "UP"
# if log2Foldchange < -0.6 and pvalue < 0.05, set as "DOWN"
results$diffexpressed[results$log2foldchange <   -0.6 & results$Rawpvalue < 0.05] <- "DOWN"
```


```{r, include=FALSE}
# Re-plot but this time color the points with "diffexpressed"
p <- ggplot(data=results, aes(x=log2foldchange, y=-log10(Rawpvalue), col=diffexpressed)) + geom_point() + theme_minimal()

# Add lines as before...
p2 <- p + geom_vline(xintercept=c(-0.6, 0.6), col="red") +
        geom_hline(yintercept=-log10(0.05), col="red")


## Change point color 

# 1. by default, it is assigned to the categories in an alphabetical order):
p3 <- p2 + scale_color_manual(values=c("blue", "black", "red"))

# 2. to automate a bit: ceate a named vector: the values are the colors to be used, the names are the categories they will be assigned to:
mycolors <- c("blue", "red", "black")
names(mycolors) <- c("DOWN", "UP", "NO")
p3 <- p2 + scale_colour_manual(values = mycolors)
```

```{r, echo=FALSE}
# Now write down the name of genes beside the points...
# Create a new column "delabel" to de, that will contain the name of genes differentially expressed (NA in case they are not)
results$delabel <- NA
results$delabel[results$diffexpressed != "NO"] <- results$genename[results$diffexpressed != "NO"]

ggplot(data=results, aes(x=log2foldchange, y=-log10(Rawpvalue), col=diffexpressed, label=delabel)) + 
    geom_point() + 
    theme_minimal() +
    geom_text() +
    geom_vline(xintercept=c(-0.6, 0.6), col="red") +
    geom_hline(yintercept=-log10(0.05), col="red")
```











```{r, include=FALSE}
Upregulatedgenes_8 = log2foldchange[log2foldchange > 0.6 ]
Downregulatedgenes_8 = log2foldchange[log2foldchange<  -0.6]

Upreg_genes_8 = attr(Upregulatedgenes_8, "names")
Downreg_genes_8= attr(Downregulatedgenes_8, "names")


```

```{r}

##From result Table
results

Upreg_8= results[results$log2foldchange > 0.6 & Rawpvalue < 0.05, ]
Upreg_8

Downreg_8 = results[results$log2foldchange <= -0.6 & Rawpvalue < 0.05, ]
Downreg_8
```







```{r, echo=FALSE}
# Finally, we can organize the labels nicely using the "ggrepel" package and the geom_text_repel() function
# load library
library(ggrepel)
# plot adding up all layers we have seen so far
ggplot(data=results, aes(x=log2foldchange, y=-log10(Rawpvalue), col=diffexpressed, label=delabel)) +
        geom_point() + 
        theme_minimal() +
        geom_text_repel() +
        scale_color_manual(values=c("blue", "black", "red")) +
        geom_vline(xintercept=c(-0.6, 0.6), col="red") +
        geom_hline(yintercept=-log10(0.05), col="red")
```

**Total Number of Upregulated genes : 3351**

**Total Number of Downregulated genes : 1840**



#################################################################################



## For Gleason Score 9

```{r, include=FALSE}
df_case_9 = subset(df_combined, gleason_score == 9 & CaseControl == "Case")

## Case


df_case_9gene = df_case_9[,1:20531]

df_case.9= df_case_9gene%>% remove_rownames %>% column_to_rownames(var="sampleID")
df_cg_9= as.data.frame(t(df_case.9))
head(df_cg_9)

```

```{r, include=FALSE}
df_c9 = cbind(df_cg_9, df_controlgene)

head(df_c9)
```



```{r, include=FALSE}
ttestgene <- function(df, grp1, grp2) {
  x = df[grp1]
  y = df[grp2]
  x = as.numeric(x)
  y = as.numeric(y)  
  results = t.test(x, y)
  results$p.value
}
Pvalue = apply(df_c9, 1, ttestgene, grp1 = c(1:137), grp2 = c(138:190))
```


```{r, include=FALSE}
control9 = apply(df_controlgene, 1, mean)
test9= apply(df_cg_9, 1, mean) 
#confirming that we have a vector of numbers
class(control9) 
class(test9)
```


```{r, include=FALSE}
#because our data is already log2 transformed, we can take the difference between the means.  And this is our log2 Fold Change or log2 Ratio == log2(control / test)
Log2FoldChange<- control9 - test9 
```


```{r, echo=FALSE}
hist(Log2FoldChange, xlab = "log2 Fold Change (Control vs Case)")
```






```{r, include=FALSE}

results = cbind(Log2FoldChange, Pvalue)
results = as.data.frame(results)
results$genename <- rownames(results)

library(ggplot2)
volcano = ggplot(data = results, aes(x = Log2FoldChange, y = -1*log10(Pvalue), label=genename))
volcano + geom_point() + geom_text(hjust=0, vjust=0) + theme_minimal() + geom_vline(xintercept=c(-0.6, 0.6), col="red") +
    geom_hline(yintercept=-log10(0.05), col="red")
  
```


```{r, include=FALSE}
# add a column of NAs
results$diffexpressed <- "NO"
# if log2Foldchange > 0.6 and pvalue < 0.05, set as "UP" 
results$diffexpressed[results$Log2FoldChange > 0.6 & results$Pvalue < 0.05] <- "UP"
# if log2Foldchange < -0.6 and pvalue < 0.05, set as "DOWN"
results$diffexpressed[results$Log2FoldChange <   -0.6 & results$Pvalue < 0.05] <- "DOWN"
```


```{r, include=FALSE}
# Re-plot but this time color the points with "diffexpressed"
p <- ggplot(data=results, aes(x=Log2FoldChange, y=-log10(Pvalue), col=diffexpressed)) + geom_point() + theme_minimal()

# Add lines as before...
p2 <- p + geom_vline(xintercept=c(-0.6, 0.6), col="red") +
        geom_hline(yintercept=-log10(0.05), col="red")


## Change point color 

# 1. by default, it is assigned to the categories in an alphabetical order):
p3 <- p2 + scale_color_manual(values=c("blue", "black", "red"))

# 2. to automate a bit: ceate a named vector: the values are the colors to be used, the names are the categories they will be assigned to:
mycolors <- c("blue", "red", "black")
names(mycolors) <- c("DOWN", "UP", "NO")
p3 <- p2 + scale_colour_manual(values = mycolors)
```

```{r, echo=FALSE}
# Now write down the name of genes beside the points...
# Create a new column "delabel" to de, that will contain the name of genes differentially expressed (NA in case they are not)
results$delabel <- NA
results$delabel[results$diffexpressed != "NO"] <- results$genename[results$diffexpressed != "NO"]

ggplot(data=results, aes(x=Log2FoldChange, y=-log10(Pvalue), col=diffexpressed, label=delabel)) + 
    geom_point() + 
    theme_minimal() +
    geom_text() +
    geom_vline(xintercept=c(-0.6, 0.6), col="red") +
    geom_hline(yintercept=-log10(0.05), col="red")
```











```{r, include=FALSE}
Upregulatedgenes_9 = Log2FoldChange[Log2FoldChange > 0.6 ]
Downregulatedgenes_9 = Log2FoldChange[Log2FoldChange<  -0.6]

Upreg_genes_9 = attr(Upregulatedgenes_9, "names")
Downreg_genes_9 = attr(Downregulatedgenes_9, "names")


```

```{r, include=FALSE}

##From result Table
results

Upreg_9= results[results$Log2FoldChange > 0.6 & Pvalue < 0.05, ]
Upreg_9

Downreg_9 = results[results$Log2FoldChange <= -0.6 & Pvalue < 0.05, ]
Downreg_9
```




**Another Version**

```{r, echo=FALSE}
# Finally, we can organize the labels nicely using the "ggrepel" package and the geom_text_repel() function
# load library
library(ggrepel)
# plot adding up all layers we have seen so far
ggplot(data=results, aes(x=Log2FoldChange, y=-log10(Pvalue), col=diffexpressed, label=delabel)) +
        geom_point() + 
        theme_minimal() +
        geom_text_repel() +
        scale_color_manual(values=c("blue", "black", "red")) +
        geom_vline(xintercept=c(-0.6, 0.6), col="red") +
        geom_hline(yintercept=-log10(0.05), col="red")
```

**Total number of Upregulated genes : 3279**
**Total number of Downregulated genes :  1956**






#####################################################################################


## For Gleason Score 10

```{r, include=FALSE}
df_case_10 = subset(df_combined, gleason_score == 10 & CaseControl == "Case")

## Case


df_case_10gene = df_case_10[,1:20531]

df_case.10= df_case_10gene%>% remove_rownames %>% column_to_rownames(var="sampleID")
df_cg_10= as.data.frame(t(df_case.10))
head(df_cg_10)

```

```{r, include=FALSE}
df_c10 = cbind(df_cg_10, df_controlgene)

head(df_c10)
```



```{r, include=FALSE}
ttestgene <- function(df, grp1, grp2) {
  x = df[grp1]
  y = df[grp2]
  x = as.numeric(x)
  y = as.numeric(y)  
  results = t.test(x, y)
  results$p.value
}
Pvalue = apply(df_c10, 1, ttestgene, grp1 = c(1:4), grp2 = c(5:57))
```


```{r, include=FALSE}
control10 = apply(df_controlgene, 1, mean)
test10= apply(df_cg_10, 1, mean) 
#confirming that we have a vector of numbers
class(control10) 
class(test10)
```


```{r, include=FALSE}
#because our data is already log2 transformed, we can take the difference between the means.  And this is our log2 Fold Change or log2 Ratio == log2(control / test)
Log2FoldChange_10<- control10 - test10
```


```{r, echo=FALSE}
hist(Log2FoldChange_10, xlab = "log2 Fold Change (Control vs Case)")
```






```{r, include=FALSE}

results = cbind(Log2FoldChange_10, Pvalue)
results = as.data.frame(results)
results$genename <- rownames(results)

library(ggplot2)
volcano = ggplot(data = results, aes(x = Log2FoldChange_10, y = -1*log10(Pvalue), label=genename))
volcano + geom_point() + geom_text(hjust=0, vjust=0) + theme_minimal() + geom_vline(xintercept=c(-0.6, 0.6), col="red") +
    geom_hline(yintercept=-log10(0.05), col="red")
  
```


```{r, include=FALSE}
# add a column of NAs
results$diffexpressed <- "NO"
# if log2Foldchange > 0.6 and pvalue < 0.05, set as "UP" 
results$diffexpressed[results$Log2FoldChange_10 > 0.6 & results$Pvalue < 0.05] <- "UP"
# if log2Foldchange < -0.6 and pvalue < 0.05, set as "DOWN"
results$diffexpressed[results$Log2FoldChange_10 <   -0.6 & results$Pvalue < 0.05] <- "DOWN"
```


```{r, include=FALSE}
# Re-plot but this time color the points with "diffexpressed"
p <- ggplot(data=results, aes(x=Log2FoldChange_10, y=-log10(Pvalue), col=diffexpressed)) + geom_point() + theme_minimal()

# Add lines as before...
p2 <- p + geom_vline(xintercept=c(-0.6, 0.6), col="red") +
        geom_hline(yintercept=-log10(0.05), col="red")


## Change point color 

# 1. by default, it is assigned to the categories in an alphabetical order):
p3 <- p2 + scale_color_manual(values=c("blue", "black", "red"))

# 2. to automate a bit: ceate a named vector: the values are the colors to be used, the names are the categories they will be assigned to:
mycolors <- c("blue", "red", "black")
names(mycolors) <- c("DOWN", "UP", "NO")
p3 <- p2 + scale_colour_manual(values = mycolors)
```

```{r, echo=FALSE}
# Now write down the name of genes beside the points...
# Create a new column "delabel" to de, that will contain the name of genes differentially expressed (NA in case they are not)
results$delabel <- NA
results$delabel[results$diffexpressed != "NO"] <- results$genename[results$diffexpressed != "NO"]

ggplot(data=results, aes(x=Log2FoldChange_10, y=-log10(Pvalue), col=diffexpressed, label=delabel)) + 
    geom_point() + 
    theme_minimal() +
    geom_text() +
    geom_vline(xintercept=c(-0.6, 0.6), col="red") +
    geom_hline(yintercept=-log10(0.05), col="red")
```











```{r, include=FALSE}
Upregulatedgenes_10 = Log2FoldChange_10[Log2FoldChange_10 > 0.6 ]
Downregulatedgenes_10 = Log2FoldChange_10[Log2FoldChange_10<  -0.6]

Upreg_genes_10 = attr(Upregulatedgenes_10, "names")
Downreg_genes_10 = attr(Downregulatedgenes_10, "names")


```

```{r, include=FALSE}

##From result Table
results

Upreg_10= results[results$Log2FoldChange_10 > 0.6 & Pvalue < 0.05, ]
Upreg_10$delabel

Downreg_10 = results[results$Log2FoldChange_10 <= -0.6 & Pvalue < 0.05, ]
Downreg_10$delabel
```






```{r, echo=FALSE}
# Finally, we can organize the labels nicely using the "ggrepel" package and the geom_text_repel() function
# load library
library(ggrepel)
# plot adding up all layers we have seen so far
ggplot(data=results, aes(x=Log2FoldChange_10, y=-log10(Pvalue), col=diffexpressed, label=delabel)) +
        geom_point() + 
        theme_minimal() +
        geom_text_repel() +
        scale_color_manual(values=c("blue", "black", "red")) +
        geom_vline(xintercept=c(-0.6, 0.6), col="red") +
        geom_hline(yintercept=-log10(0.05), col="red")
```

**Total Upregulated genes : 932**
**Total Downregulated genes : 539**






















###Overall differential Expression


```{r, include=FALSE}
genes_7= c(Upreg_7$delabel, Downreg_7$delabel)
genes_8= c(Upreg_8$delabel, Downreg_8$delabel)
genes_9= c(Upreg_9$delabel, Downreg_9$delabel)
genes_10 = c(Upreg_10$delabel, Downreg_10$delabel)

x <- list(GS_7= genes_7, 
          GS_8= genes_8, 
          GS_9= genes_9,
          GS_10 =genes_10)
```


```{r, include=FALSE}
if (!require(devtools)) install.packages("devtools")
devtools::install_github("gaospecial/ggVennDiagram")
```


```{r, include=FALSE}
result= intersect(genes_7, genes_8)
Common_genes= intersect(result, genes_9)
Com_genes_1 = intersect(Common_genes, genes_10)

Com_genes_1
```

```{r, include=FALSE}

print(Com_genes_1)
```




```{r, include=FALSE}
write.csv(Com_genes_1, file = "CommonGenes_new.csv")

```



```{r,include=FALSE}

library("ggVennDiagram")
# Remove labels background color
ggVennDiagram(x, label_alpha = 0) + 
ggplot2::scale_fill_gradient(low="blue",high = "yellow")
```

### Common Upregulated genes

```{r, include=FALSE}
genes_7_up= c(Upreg_7$delabel)
genes_8_up= c(Upreg_8$delabel)
genes_9_up= c(Upreg_9$delabel)
genes_10_up = c(Upreg_10$delabel)

x_up <- list(GS_7_up= genes_7_up, 
          GS_8_up= genes_8_up, 
          GS_9_up= genes_9_up,
          GS_10_up =  genes_10_up)
```





```{r, include=FALSE}
C1= intersect(genes_7_up, genes_8_up)
C2= intersect(C1, genes_9_up)
Common_Up = intersect(C2, genes_10_up)

Common_Up
```





```{r, echo=FALSE}

# Remove labels background color
ggVennDiagram(x_up, label_alpha = 0) + 
ggplot2::scale_fill_gradient(low="blue",high = "yellow")
```




### Common Downregulated genes

```{r, include=FALSE}
genes_7_down= c(Downreg_7$delabel)
genes_8_down= c(Downreg_8$delabel)
genes_9_down= c(Downreg_9$delabel)
genes_10_down = c(Downreg_10$delabel)

x_down <- list(GS_7_down= genes_7_down, 
          GS_8_down= genes_8_down, 
          GS_9_down= genes_9_down,
          GS_10_down =  genes_10_down)
```



```{r, include=FALSE}
c1= intersect(genes_7_down, genes_8_down)
c2 = intersect(c1, genes_9_down)
Common_down= intersect(c2, genes_10_down)


Common_down
```



```{r, echo=FALSE}
# Remove labels background color
ggVennDiagram(x_down, label_alpha = 0) + 
ggplot2::scale_fill_gradient(low="blue",high = "yellow")
```





```{r, include=FALSE}
Com_genes= list(Common_Up, Common_down)
```


```{r, include=FALSE}
write.csv(Com_genes, file = "CommonGenes_new.csv")

```





`


**Venn Diagram of GS7 and GS8**


```{r, echo=FALSE}

x1= list(Downreg_7$delabel, Upreg_7$delabel, Downreg_8$delabel, Upreg_8$delabel)
# Change category names
# Change the gradient fill color
ggVennDiagram(
  x1, label_alpha = 0,
  category.names = c(" Downreg 7"," Upreg 7", " Downreg 8", " Upreg 8")
  ) +
  ggplot2::scale_fill_gradient(low="blue",high = "yellow")
```


```{r, include=FALSE}
## Finding the gene list who are Upregulated in both GS7 and GS8

CommonUpreg_78= intersect(Upreg_7$delabel, Upreg_8$delabel)
CommonUpreg_78
```


```{r, include=FALSE}
## Finding the gene list who are Downregulated in both GS7 and GS8


CommonDownreg_78 = intersect(Downreg_7$delabel, Downreg_8$delabel)
CommonDownreg_78

```

**gene list who are Upregulated in GS7 but Downregulated  in GS8**

```{r, echo=FALSE}
## Finding the gene list who are Upregulated in GS7 but Downregulated  in GS8
CommonU7D8= intersect(Upreg_7$delabel, Downreg_8$delabel)
CommonU7D8

```

**gene list who are Downregulated in GS7 but Upregulated in GS8**

```{r, echo=FALSE}
## Finding the gene list who are Downregulated in GS7 but Upregulated in GS8
CommonD7U8 = intersect(Downreg_7$delabel, Upreg_8$delabel)
CommonD7U8


```




**Venn Diagram of GS7 and GS9**


```{r, echo=FALSE}

x1= list(Downreg_7$delabel, Upreg_7$delabel, Downreg_9$delabel, Upreg_9$delabel)
# Change category names
# Change the gradient fill color
ggVennDiagram(
  x1, label_alpha = 0,
  category.names = c(" Downreg 7"," Upreg 7", " Downreg 9", " Upreg 9")
  ) +
  ggplot2::scale_fill_gradient(low="blue",high = "yellow")
```


```{r, include=FALSE}
## Finding the gene list who are Upregulated in both GS7 and GS9
CommonUpreg_79= intersect(Upreg_7$delabel, Upreg_9$delabel)
CommonUpreg_79

## Finding the gene list who are Downregulated in both GS7 and GS9
CommonDownreg_79 = intersect(Downreg_7$delabel, Downreg_9$delabel)
CommonDownreg_79

```

**gene list who are Upregulated in GS7 but Downregulated in GS9**

```{r, echo=FALSE}
## Finding the gene list who are Upregulated in GS7 but Downregulated in GS9
CommonU7D9= intersect(Upreg_7$delabel, Downreg_9$delabel)
CommonU7D9
```

**gene list who are Downregulated in GS7 but Upregulated in GS9**

```{r, echo=FALSE}
## Finding the gene list who are Downregulated in GS7 but Upregulated in GS9
CommonD7U9 = intersect(Downreg_7$delabel, Upreg_9$delabel)
CommonD7U9


```


**Venn Diagram of GS7 and GS10**


```{r, echo=FALSE}

x1= list(Downreg_7$delabel, Upreg_7$delabel, Downreg_10$delabel, Upreg_10$delabel)
# Change category names
# Change the gradient fill color
ggVennDiagram(
  x1, label_alpha = 0,
  category.names = c(" Downreg 7"," Upreg 7", " Downreg 10", " Upreg 10")
  ) +
  ggplot2::scale_fill_gradient(low="blue",high = "yellow")
```


```{r, include=FALSE}
## Finding the gene list who are Upregulated in both GS7 and GS10
CommonUpreg_710= intersect(Upreg_7$delabel, Upreg_10$delabel)
CommonUpreg_710

## Finding the gene list who are Downregulated in both GS7 and GS10
CommonDownreg_710 = intersect(Downreg_7$delabel, Downreg_10$delabel)
CommonDownreg_710

```

**gene list who are Upregulated in GS7 but Downregulated in GS10**

```{r, echo=FALSE}
## Finding the gene list who are Upregulated in GS7 but Downregulated in GS10
CommonU7D10= intersect(Upreg_7$delabel, Downreg_10$delabel)
CommonU7D10
```

**gene list who are Downregulated in GS7 but Upregulated in GS10**

```{r, echo=FALSE}
## Finding the gene list who are Downregulated in GS7 but Upregulated in GS10
CommonD7U10 = intersect(Downreg_7$delabel, Upreg_10$delabel)
CommonD7U10


```










**Venn Diagram of GS8 and GS9**


```{r, echo=FALSE}

x1= list(Downreg_8$delabel, Upreg_8$delabel, Downreg_9$delabel, Upreg_9$delabel)
# Change category names
# Change the gradient fill color
ggVennDiagram(
  x1, label_alpha = 0,
  category.names = c(" Downreg 8"," Upreg 8", " Downreg 9", " Upreg 9")
  ) +
  ggplot2::scale_fill_gradient(low="blue",high = "yellow")
```


```{r, include=FALSE}
## Finding the gene list who are Upregulated in both GS8 and GS9
CommonUpreg_89= intersect(Upreg_8$delabel, Upreg_9$delabel)
CommonUpreg_89

## Finding the gene list who are Upregulated in both GS8 and GS9
CommonDownreg_89 = intersect(Downreg_8$delabel, Downreg_9$delabel)
CommonDownreg_89

```


**gene list who are Upregulated in GS8 but Downregulated in GS9**

```{r, echo=FALSE}
## Finding the gene list who are Upregulated in GS8 but Downregulated in GS9
CommonU8D9= intersect(Upreg_8$delabel, Downreg_9$delabel)
CommonU8D9

```
**gene list who are Downregulated in GS8 but Upregulated in GS9**

```{r}
## Finding the gene list who are Downregulated in GS8 but Upregulated in GS9
CommonD8U9 = intersect(Downreg_8$delabel, Upreg_9$delabel)
CommonD8U9


```




**Venn Diagram of GS8 and GS10**


```{r, echo=FALSE}

x1= list(Downreg_8$delabel, Upreg_8$delabel, Downreg_10$delabel, Upreg_10$delabel)
# Change category names
# Change the gradient fill color
ggVennDiagram(
  x1, label_alpha = 0,
  category.names = c(" Downreg 8"," Upreg 8", " Downreg 10", " Upreg 10")
  ) +
  ggplot2::scale_fill_gradient(low="blue",high = "yellow")
```


```{r, include=FALSE}
## Finding the gene list who are Upregulated in both GS8 and GS10
CommonUpreg_810= intersect(Upreg_8$delabel, Upreg_10$delabel)
CommonUpreg_810

## Finding the gene list who are Upregulated in both GS8 and GS9
CommonDownreg_810 = intersect(Downreg_8$delabel, Downreg_10$delabel)
CommonDownreg_810

```


**gene list who are Upregulated in GS8 but Downregulated in GS9**

```{r, echo=FALSE}
## Finding the gene list who are Upregulated in GS8 but Downregulated in GS9
CommonU8D10= intersect(Upreg_8$delabel, Downreg_10$delabel)
CommonU8D10

```



**gene list who are Downregulated in GS8 but Upregulated in GS9**

```{r, echo=FALSE}


## Finding the gene list who are Downregulated in GS8 but Upregulated in GS9
CommonD8U10 = intersect(Downreg_8$delabel, Upreg_10$delabel)
CommonD8U10


```




**Venn Diagram of GS9 and GS10**


```{r, echo=FALSE}

x1= list(Downreg_9$delabel, Upreg_9$delabel, Downreg_10$delabel, Upreg_10$delabel)
# Change category names
# Change the gradient fill color
ggVennDiagram(
  x1, label_alpha = 0,
  category.names = c(" Downreg 9"," Upreg 9", " Downreg 10", " Upreg 10")
  ) +
  ggplot2::scale_fill_gradient(low="blue",high = "yellow")
```



```{r, include=FALSE}
## Finding the gene list who are Upregulated in both GS9 and GS10
CommonUpreg_910= intersect(Upreg_9$delabel, Upreg_10$delabel)
CommonUpreg_910

## Finding the gene list who are Upregulated in both GS9 and GS9
CommonDownreg_910 = intersect(Downreg_9$delabel, Downreg_10$delabel)
CommonDownreg_910

```

**gene list who are Upregulated in GS9 but Downregulated in GS10**

```{r,echo=FALSE}
## Finding the gene list who are Upregulated in GS9 but Downregulated in GS10
CommonU9D10= intersect(Upreg_9$delabel, Downreg_10$delabel)
CommonU9D10

```

**gene list who are Downregulated in GS9 but Upregulated in GS10**

```{r, echo=FALSE}
## Finding the gene list who are Downregulated in GS9 but Upregulated in GS10
CommonD9U10 = intersect(Downreg_9$delabel, Upreg_10$delabel)
CommonD9U10


```









```{r, include=FALSE}

x1= list(Downreg_7$delabel, Upreg_7$delabel, Downreg_8$delabel, Upreg_8$delabel, Downreg_9$delabel, Upreg_9$delabel, Downreg_10$delabel, Upreg_10$delabel)
# Change category names
# Change the gradient fill color
plotVenn(x1)
```






```{r, include=FALSE}

##New data with differentially expressed genes

Common_genes_new = c(Common_Up, Common_down)
```



```{r, include=FALSE}


##New dataset with selected genes
myvar= c("sampleID", Common_genes_new)
dat= data2[,myvar] 
dat
```





```{r, include=FALSE}
##Control

df_controlgene
df_cont=as.data.frame(t(df_controlgene))

dat_control= df_cont
dat_control= tibble::rownames_to_column(dat_control, "sampleID")
dat_control$sampleID = as.character(dat_control$sampleID)

dat_control

dat_conTl= dat_control[,myvar]

dat_conTl





```


```{r, include=FALSE}
dat_con= dat_conTl%>% remove_rownames %>% column_to_rownames(var="sampleID")

dat_con
```






```{r, include=FALSE}
## Joining the tables by sampleID

dat_combined= dat %>%  inner_join(df_clinical, by = "sampleID") %>%
                        inner_join(df_survival, by ="sampleID")


dim(dat_combined)
dat_combined

```



```{r, include=FALSE}
## Dividing by case and control of data
dat_combined <- dat_combined %>%
  add_column(CaseControl = 
               if_else(.$sample_type == "Primary Tumor", "Case", "Control"),
             .after="RGS10")



```




```{r, include=FALSE}
write.csv(dat_combined, file = "combined_data.csv")

```




```{r, include=FALSE}
##Genes extracted from Random forest and Ridge Regression Model.

genes_RR= c('DLX2', 'F2RL2', 'ITGAX', 'KCNG3', 'LHX6', 'LOC100128842', 'RAB17', 'RPS26')
```

**Common Up Regulated genes of this method, Random forest and Ridge Regression Model**


```{r, echo=FALSE}
intersect(Common_Up, genes_RR)
```

**Common Down Regulated genes of this method, Random forest and Ridge Regression Model**

```{r, echo=FALSE}
intersect(Common_down, genes_RR)
```

```{r, include=FALSE}
genes_RF = c('HFE', 'MARCKSL1', 'DLX2', 'RHBDL3', 'LY6D', 'DLX1', 'RPS26', 'SIM2',
       'KRT5', 'ZNF488', 'LRRC56', 'KANK4', 'ASPH', 'ZDHHC15', 'CDK5R1',
       'ATP1B1', 'RAB17', 'EZH2', 'ITGAX', 'SEMA6D', 'METTL7A', 'FZD8',
       'SEMG1', 'CALML3', 'TSPAN13', 'LRFN1', 'KCNG3', 'CPNE6', 'F2RL2',
       'C13orf38', 'LHX6', 'CIDEC', 'C2orf88', 'CRYZ', 'PPARGC1A', 'DLGAP5',
       'NCAPG', 'RPE65', 'FABP7', 'PCDHA1', 'ABHD6', 'BMP7', 'BEX1', 'CXCR2',
       'CDC20', 'LOC100128842', 'MORC1', 'FAM72B', 'KCNF1')
```


**Common Up Regulated genes of this method, Random forest Model**


```{r, echo=FALSE}
intersect(Common_Up, genes_RF)
```

**Common Down Regulated genes of this method, Random forest Model**

```{r, echo=FALSE}
intersect(Common_down, genes_RF)
```












